Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-04-14 src/tex/ms.tex
Explicitly mention that h is the Planck constant.

\citet{Wang_2021} performed \ac{PE} on GWTC-1 events with a frequency-dependent model of birefringence resembling ours.
Following \cite{Zhao:2019xmm}, that reference parameterized the birefringent waveform in terms of some amplitude and phase modifications to the linear polarizations ($\delta h$ and $\delta \Psi$ respectively), such that
\begin{equation}
    h_{+/\times}^{\rm BR}(f) = h_{+/\times}^{\rm GR}(f)\mp h_{\times/+}^{\rm GR}(f)(i\delta h-\delta\Psi)\,,
\end{equation}
with the plus (minus) sign for the cross (plus) polarization.
In terms of circular polarizations, this is equivalent to 
\begin{align}
h^{\rm BR}_{L/R}(f) &= h^{\rm GR}_{L/R}(f) \left(1 \mp \delta h \mp i \delta \Psi \right) \nonumber\\
&\approx h^{\rm GR}_{L/R}(f) \exp(\mp \delta h \mp i \delta \Psi) \, ,
\end{align}
assuming a small $\delta h$ and $\delta \Psi$ in the last line.
To consider only amplitude birefringence, as in this work, we must compare to the result in Ref.~\citep{Wang_2021} that set $\delta \Psi = 0$ and parameterized $\delta h = \pi f z / M_{\rm PV}$, where $M_{\rm PV}$ is the energy scale of the birefringent (parity-violating) correction.%
\footnote{Concretely, \citet{Wang_2021} write $\delta h = - A_\nu \pi f$ with $A_\nu = M_{\rm PV}^{-1} \left[\alpha_\nu (z=0) - \alpha_\nu(z) \left(1+z\right)\right]$, for $\alpha_\nu$ some function of redshift encoding the evolution of a birefringence-mediating field; to produce their constraint, however, they further set $\alpha_\nu(z) = 1$, yielding $A_\nu = -z / M_{\rm PV}$ and hence $\delta h = \pi f z / M_{\rm PV}$.}
Comparing to our Eq.~\eqref{eq:waveform_modification} and approximating $z \approx d_C H_0/c$ via the Hubble constant, $H_0$, this means
\begin{equation}
    |\kappa| \simeq \frac{\pi H_0}{c} \frac{h \left( 100 \, \mathrm{Hz} \right)}{M_{\rm PV}} \simeq \frac{3.0 \times 10^{-22} \, \mathrm{GeV}}{M_\mathrm{PV}} \, \mathrm{Gpc}^{-1}
\end{equation}
\citet{Wang_2021} quote a constraint of $M_{\rm PV} > 10^{-22}\, {\rm GeV}$ at 90\% credibility, which translates into \variable{output/kappa_Wang.txt}.
We obtained a tighter 90\% upper limit of \variable{output/restricted_absolute_kappa_90.txt}, or \variable{output/M_PV_constraint.txt}.

>>>>

\citet{Wang_2021} performed \ac{PE} on GWTC-1 events with a frequency-dependent model of birefringence resembling ours.
Following \cite{Zhao:2019xmm}, that reference parameterized the birefringent waveform in terms of some amplitude and phase modifications to the linear polarizations ($\delta h$ and $\delta \Psi$ respectively), such that
\begin{equation}
    h_{+/\times}^{\rm BR}(f) = h_{+/\times}^{\rm GR}(f)\mp h_{\times/+}^{\rm GR}(f)(i\delta h-\delta\Psi)\,,
\end{equation}
with the plus (minus) sign for the cross (plus) polarization.
In terms of circular polarizations, this is equivalent to 
\begin{align}
h^{\rm BR}_{L/R}(f) &= h^{\rm GR}_{L/R}(f) \left(1 \mp \delta h \mp i \delta \Psi \right) \nonumber\\
&\approx h^{\rm GR}_{L/R}(f) \exp(\mp \delta h \mp i \delta \Psi) \, ,
\end{align}
assuming a small $\delta h$ and $\delta \Psi$ in the last line.
To consider only amplitude birefringence, as in this work, we must compare to the result in Ref.~\citep{Wang_2021} that set $\delta \Psi = 0$ and parameterized $\delta h = \pi f z / M_{\rm PV}$, where $M_{\rm PV}$ is the energy scale of the birefringent (parity-violating) correction.%
\footnote{Concretely, \citet{Wang_2021} write $\delta h = - A_\nu \pi f$ with $A_\nu = M_{\rm PV}^{-1} \left[\alpha_\nu (z=0) - \alpha_\nu(z) \left(1+z\right)\right]$, for $\alpha_\nu$ some function of redshift encoding the evolution of a birefringence-mediating field; to produce their constraint, however, they further set $\alpha_\nu(z) = 1$, yielding $A_\nu = -z / M_{\rm PV}$ and hence $\delta h = \pi f z / M_{\rm PV}$.}
Comparing to our Eq.~\eqref{eq:waveform_modification} and approximating $z \approx d_C H_0/c$ via the Hubble constant, $H_0$, this means
\begin{equation}
    |\kappa| \simeq \frac{\pi H_0}{c} \frac{h \left( 100 \, \mathrm{Hz} \right)}{M_{\rm PV}} \simeq \frac{3.0 \times 10^{-22} \, \mathrm{GeV}}{M_\mathrm{PV}} \, \mathrm{Gpc}^{-1},
\end{equation}
where $h$ is Planck's constant.
\citet{Wang_2021} quote a constraint of $M_{\rm PV} > 10^{-22}\, {\rm GeV}$ at 90\% credibility, which translates into \variable{output/kappa_Wang.txt}.
We obtained a tighter 90\% upper limit of \variable{output/restricted_absolute_kappa_90.txt}, or \variable{output/M_PV_constraint.txt}.
